Comparative effectiveness of ChAdOx1 versus BNT162b2 COVID-19 vaccines in Health and Social Care workers in England: a cohort study using OpenSAFELY

### 2021-10-13 manuscript/draft-manuscript.Rmd
update manuscript, readme

---
title: "Comparative effectiveness of ChAdOx1 versus BNT162b2 COVID-19 vaccines in Health and Social Care workers in England: a cohort study using OpenSAFELY"
output:
  pdf_document:
    toc: no
  html_document:
    keep_md: yes
    self_contained: yes
  bookdown::html_document2:
    number_sections: no
    toc: no
  word_document: default
bibliography: references.bib
csl: vancouver.csl
link-citations: yes
zotero: yes
header-includes:
- \usepackage{float} 
- \floatplacement{figure}{H}
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \captionsetup[table]{labelformat=empty}
---

@@

This study found no substantial differences in the incidence of SARS-CoV-2 infection or COVID-19-related hospital events following vaccination with BNT162b2 or ChAdOx1 in a cohort of health and social care workers in England. The incidence of COVID-19-related A&E attendances or hospital admissions four weeks after the first dose of either vaccine was fewer than one event in 10,000-person-years, suggesting strong protective effects for both vaccines but nevertheless limiting power to reliably estimate comparative effectiveness with respect to severe COVID-19 outcomes. Further studies are needed to assess comparative effectiveness in newer, more prevalent variants.

>>>>

---
title: "Comparative effectiveness of ChAdOx1 versus BNT162b2 COVID-19 vaccines in Health and Social Care workers in England: a cohort study using OpenSAFELY"
output:
  word_document: default
  html_document:
    keep_md: yes
    self_contained: yes
  bookdown::html_document2:
    number_sections: no
    toc: no
  pdf_document:
    toc: no
bibliography: references.bib
csl: vancouver.csl
link-citations: yes
zotero: yes
header-includes:
- \usepackage{float} 
- \floatplacement{figure}{H}
- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \captionsetup[table]{labelformat=empty}
---

@@

This study found no substantial differences in the incidence of SARS-CoV-2 infection or COVID-19-related hospital events following vaccination with BNT162b2 or ChAdOx1 in a cohort of health and social care workers in England. The incidence of COVID-19-related A&E attendances or hospital admissions four weeks after the first dose of either vaccine was fewer than one event in 10,000-person-years, suggesting strong protective effects for both vaccines but nevertheless limiting power to reliably estimate comparative effectiveness with respect to severe COVID-19 outcomes. Further studies are needed to assess comparative effectiveness in newer, more prevalent variants and to assess longer-term effectiveness.
